Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-23 longoutput.tex
Use auto-indent
Fix typo
Fix another typo
Fix mistake in kernel proof

\begin{proof}
	Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now nonsider some $\tilde{t}$ such that $\ket\phi\bra{\tilde{t}}\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\ket\phi\bra{\tilde{t+1}}=U_{t+1}\ket\phi\bra{\tilde{t}}$ for $t\ne T$, and $\ket\phi\bra{\tilde{t}}=U_t\ket\phi\bra{\tilde{t-1}}$ for $t\ne0$. So we can obtain the required statement by induction.
\end{proof}

@@

\begin{algorithm}
	\caption{Check for ground state}
	\begin{algorithmic}[1]
		\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
		\State $p_S=\frac{|d_S|}{D}$
		\State $\tilde{S}\gets$ Pick weighted using $p_S$
		\State $\lambda_{\tilde{S}}\gets$ Measure $\ket\phi$ in the $\tilde{S}$ basis
		\If{$\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$}
			\State Accept
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}

\begin{align*}
	\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
	&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\E[\lambda_{\tilde{S}}]]\\
	&=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]
\end{align*}

Note that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}=-1$.

$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\tilde{S}}[\sgn(d_{\tilde{S}})\lambda_{\tilde{S}}]=-p+(1-p)$$
\begin{align*}
	\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
	&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
\end{align*}

@@

\begin{theorem}
Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
\begin{itemize}
	\item has $t$ terms
	\item acts on $q$ qubits
	\item Ground state $0$...?
	\item Something something $\frac{3}{4}$?
\end{itemize}
Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$. We now decomposite the input in this basis.

@@

Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decomposite the input as
$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$

>>>>

	\begin{proof}
		Let $\ket\phi\in K_{clock}\cap K_{prop}$. As $\ket\phi\in K_{clock}$, the time register components are always valid unary representations. Now consider some $\widetilde{t}$ such that $\bra{\widetilde{t}}\ket\phi\ne0$. As $\ket\phi\in K_{prop}$, we can then say that $\bra{\widetilde{t+1}}\ket\phi=\bra{\widetilde{t}}U_{t+1}\ket\phi$ for $t\ne T$, and $\bra{\widetilde{t}}\ket\phi=U_t\bra{\widetilde{t-1}}\ket\phi$ for $t\ne0$. So we can obtain the required statement by induction.
	\end{proof}

@@

	\begin{algorithm}
		\caption{Check for ground state}
		\begin{algorithmic}[1]
			\State $D\gets\sum_{S\in\mathcal{G}_{XZ}}|d_S|$
			\State $p_S=\frac{|d_S|}{D}$
			\State $\widetilde{S}\gets$ Pick weighted using $p_S$
			\State $\lambda_{\widetilde{S}}\gets$ Measure $\ket\phi$ in the $\widetilde{S}$ basis
			\If{$\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$}
			\State Accept
			\Else
			\State Reject
			\EndIf
		\end{algorithmic}
	\end{algorithm}

	\begin{align*}
		\frac{1}{D}\braket{\phi|H|\phi}&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\braket{\phi|S|\phi}\\
		&=\sum_{S\in\mathcal{G}_{XZ}} p_S\sgn(d_S)\E[\lambda_S]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\E[\lambda_{\widetilde{S}}]]\\
		&=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]
	\end{align*}

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.

	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$. We now decompose the input in this basis.

@@

	Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decompose the input as
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
